Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-09-13 tex/WW4C_VHzQ.tex

In this paper we include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017 and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (200910..) to 1st April 2016, to get as much coverage as
possible. Hence, the NIR coverage is extremely heterogeneous.

@@

    Add a new entry \verb+RequiredMatchedApertureProduct+

    \begin{itemize}
    \item mapID	archiveName	programmeID	extractor	mapType	name	description	selection	finalProductTable	addSurveyList
    \item 1	1	WSA	10999	CASU	2	highzQsoMap	Variability via matched apertures for set of high-z QSOs	SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue	highzQsoMapVariability	NONE
    \end{itemize}

    Explain

    Entries in \verb+RequiredMapAverages+

    Add table?
    \begin{table*}
      \begin{center}
        \setlength{\tabcolsep}{4pt}
        \begin{tabular}{lll lll lll l}
          \hline \hline
          &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
          \hline
          1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
          2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
          3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
          4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
          5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
          6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
          \hline \hline
          \label{tab:The_Numbers}
        \end{tabular}
        \caption{}
      \end{center}
    \end{table*}

>>>>

In this paper we include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017 and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (20091015) to 1st April 2016, to get as much coverage as
possible. Hence, the NIR coverage is extremely heterogeneous.

@@

To create matched aperture products it is first necessary to define the product. We do this in two requirements tables, \verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+ that
tell the \textbf{ProgrammeBuilder} software which tables to create and what type of product is being created. These requirements tables also drive the pipeline.

\verb+RequiredMatchedApertureProduct+ contains the following attributes for the High-z QSO MAP product.
\begin{itemize}
    \item mapID, Identifier of the MAP product, value=1	
    \item archiveName, Main archive of product, value='VSA'/'WSA' 	
    \item programmeID, UID of programme, in this case a combined programme, value=10999
    \item extractor, Extractor used for forced photometry, value='CASU' (imcore_list)
    \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
    \item name, Name of MAP product, value='highzQsoMap'
    \item description, Description of MAP product, 'Variability via matched apertures for set of high-z QSOs'	
    \item selection, Selection, e.g. File, pseudo-SQL, FITS image that is used to give input list, value='SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue'	
    \item finalProductTable, Name of final product table, value='highzQsoMapVariability'
    \item addSurveyList, List of additional archive/surveys that data comes from, value='NONE'
\end{itemize}

\verb+RequiredMatchedApertureProduct+ gives all of the information such as the {\it programmeID} (identifying which data), the {\it mapType} (type of processing), the {\it extractor} to use, the input list {\it selection}, which in this case is the IDs and positions of the QSOs in \verb+finalQsoCatalogue+ which contains all the literature data and pre-derived parameters for the 424 QSOs.

\verb+RequiredMapAverages+ is used to setup the averaging of the MAP photometry from several images. We can average the epochs in multiple ways: over all the input images to a deep image, or similarly the input pawprint images to tile image in VISTA. Alternatively we can average over a fixed number of epochs or a fixed duration in time. Multiple setups can be defined in \verb+RequiredMapAverages+, and the different averages selected using the defined {\it setupID}.

    Add table?
    \begin{table*}
      \begin{center}
        \setlength{\tabcolsep}{4pt}
        \begin{tabular}{ll lll lll l}
          \hline \hline
   programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
          \hline
10999	& 1 & 0 & Average over whole time & 0 &	NONE &	-1.000000 &	-99999999 &	1 \\
10999	& 1 & 1 & Average over a week &	0 & NONE & +7.000000 &	-99999999 &	1\\
10999	& 1 & 2	& Average over a fortnight & 0 & NONE &	+14.000000 & -99999999 & 1\\
10999	& 1 & 3	& Average over a month & 0 & NONE & +30.000000 & -99999999 & 1\\
10999	& 1 & 4	& Average over 10 epochs & 0 & NONE & -9.999995E008 & 10 & 1\\
10999	& 1 & 5 & Average over 6 months	& 0 & NONE & +183.000000 & -99999999 & 1 \\
10999	& 1 & 6	& Average over 1 year &	0 & NONE & +365.000000 & -99999999 & 1 \\
10999	& 1 & 7	& Average over 2 years & 0 & NONE & +730.000000	& -99999999 & 1 \\
10999	& 1 & 8 & Average over 3 months & 0 & NONE & +91.000000	& -99999999 & 1 \\
          \hline \hline
          \label{tab:The_Numbers}
        \end{tabular}
        \caption{}
      \end{center}
    \end{table*}
